\emph{Light Exposure Behavior Assessment (LEBA)}: Develop of a novel instrument to capture light exposure-related behaviours

### 2021-09-10 manuscript.Rmd

```{r setup, include = FALSE}
library(papaja) # devtools::install_github("crsh/papaja")
library(lavaan)
library(semPlot) #devtools::install_github('SachaEpskamp/semPlot',  dependencies = T)
library(semTools)
library(MOTE)
library(psych)
library(dlookr)
library(tidyverse)
library(qgraph)
library(kableExtra)
library(paran) # Parallel analysis
library(EFA.MRFA) # Hull method
library(DiagrammeR) #devtools::install_github('rich-iannone/DiagrammeR')
library(DiagrammeRsvg) #For DiagrammeR
library(rsvg) #For DiagrammeR
library(correlation)
library(ggcorrplot)
library(car) #Reversecoding
library(Hmisc)
library(semTable)

@@

```{r preparingData, include=FALSE}
data <- readRDS("leba_2021-09-03.rds")

@@

## Merge "0"s and "1"s into "1"s 9select,subset assign)
descriptives.data[ , 6:53 ][ descriptives.data[ , 6:53 ] == 0 ] <- 1
EFA.descriptives <- descriptives.data[1:428,]
CFA.descriptives <- descriptives.data[429:690, ]

#Separating the EFA and CFA(only items)
sem.data <- data[, 6:53] #EFA & CFA data
sem.data[ sem.data == 0] <- 1 #Merged "0"s and "1"s into "1"s

@@

export_svg(Flowchart1) %>%
  charToRaw() %>%
  rsvg() %>%
  png::writePNG("Flowchart1.png")

@@

```{r FlowchartFig,  out.width = '100%', out.height= '100%', fig.align = 'center', fig.cap='Development and psychometric properties of LEBA '}
knitr::include_graphics('Flowchart1.png')
```

@@

# Parallel analysis
 paran(correlations$rho, iterations=500, centile=0, quietly=FALSE,
      status=TRUE, all=FALSE, cfa=FALSE, graph=TRUE,
      color=TRUE, col=c("black","red","blue"),
      lty=c(1,2,3), lwd=1, legend=TRUE, file="parallel.png",
      width=640, height=640, grdevice=png, seed=0, mat=NA, n=NA)

# HULL
hullEFA(EFA.data,extr = "ULS", index_hull = "CAF", display = TRUE, graph = TRUE,
        details = TRUE)

@@

```{r factor_identification_fig, eval=FALSE, fig.align='center', fig.cap='Factor Identification (A) Parallel analysis (B) Scree Plot, fig.ncol=2, warning=FALSE, (C) Hull method', fig.show="hold", include=FALSE, out.height="50%", out.width="50%"}
knitr::include_graphics('parallel.png')
scree(correlations$rho,factors=TRUE,pc=TRUE,main="(B)",
      hline=NULL,add=F)
knitr::include_graphics('HUll method.jpeg')

@@

export_svg(EFAplot.LR) %>%
  charToRaw() %>%
  rsvg() %>%
  png::writePNG("EFAplot.LR.png")

@@

```{r EFAplot, eval=FALSE, fig.align='center', fig.cap='Five Factor Solution', warning=FALSE, include=FALSE, out.height="100%", out.width="120%"}
knitr::include_graphics('EFAplot.LR.png')

@@

```{r Invarianceshortcut}
#library("semTools")
invariance.model <- measurementInvariance(model = LB.model.Cor.2,
                                          data = invariance.data,
                                          group = "English_Speaking",
                                          ordered =   names(CFA.data),
                                          estimator = "WLSMV",
                                          strict = T)
invariance.model$fit.configural
```

>>>>

```{r dependencymanager, include = FALSE}
library(packrat)
packrat::init()
```

```{r setup}

knitr::opts_chunk$set(include = FALSE)
library(papaja) # devtools::install_github("crsh/papaja")
library(lavaan)
library(semPlot) #devtools::install_github('SachaEpskamp/semPlot',  dependencies = T)
library(semTools)
library(MOTE)
library(psych)
library(dlookr)
library(tidyverse)
library(qgraph)
library(kableExtra)
library(paran) # Parallel analysis
library(EFA.MRFA) # Hull method
library(DiagrammeR) #devtools::install_github('rich-iannone/DiagrammeR')
library(DiagrammeRsvg) #For DiagrammeR
library(rsvg) #For DiagrammeR
#library(correlation)
library(ggcorrplot)
library(car) #Reversecoding
library(semTable)

@@

```{r preparingData, include=FALSE}
data <- readRDS("leba_2021-09-08.rds")

@@

## Merge "0"s and "1"s into "1"s 9select,subset assign)
descriptives.data[ , 9:56 ][ descriptives.data[ , 9:56 ] == 0 ] <- 1
EFA.descriptives <- descriptives.data[1:428,]
CFA.descriptives <- descriptives.data[429:690, ]

#Separating the EFA and CFA(only items)
sem.data <- data[, 9:56] #EFA & CFA data
sem.data[ sem.data == 0] <- 1 #Merged "0"s and "1"s into "1"s

@@

export_svg(Flowchart1) %>%
  charToRaw() %>%
  rsvg() %>%
  png::writePNG("mFlowchart1.png")

@@

```{r FlowchartFig, fig.align='center', fig.cap='Development', include=FALSE, out.height='100%', out.width='100%'}
knitr::include_graphics('Manuscript.figures/Flowchart1.png')
```

@@

# Parallel analysis
paran(correlations$rho, iterations=500, centile=0, quietly=FALSE,
      status=TRUE, all=FALSE, cfa=FALSE, graph=TRUE,
      color=TRUE, col=c("black","red","blue"),
      lty=c(1,2,3), lwd=1, legend=TRUE, file="Manuscript.figures/parallel.png",
      width=640, height=640, grdevice=png, seed=0, mat=NA, n=NA)

# HULL
hullEFA(EFA.data,extr = "ULS", index_hull = "CAF", display = TRUE, graph = T,
        details = TRUE)

@@

```{r factor_identification_fig, eval=FALSE, fig.align='center', fig.cap='Factor Identification (A) Parallel analysis (B) Scree Plot, fig.ncol=2, warning=FALSE, (C) Hull method', fig.show="hold", include=FALSE, out.height="50%", out.width="50%"}
knitr::include_graphics('Manuscript.figures/parallel.png')
scree(correlations$rho,factors=TRUE,pc=TRUE,main="(B)",
      hline=NULL,add=F)
knitr::include_graphics('Manuscript.figures/Hull.png')

@@

export_svg(EFAplot.LR) %>%
  charToRaw() %>%
  rsvg() %>%
  png::writePNG("Manuscript.figures/EFAplot.LR.png")

@@

```{r EFAplot, fig.align='center', fig.cap='Five Factor Solution', warning=FALSE, include=FALSE, out.height="100%", out.width="120%"}
knitr::include_graphics('Manuscript.figures/EFAplot.LR.png')

@@

```{r Invarianceshortcut, include=FALSE}
#library("semTools")
invariance.model <- measurementInvariance(model = LB.model.Cor.2,
                                          data = invariance.data,
                                          group = "English_Speaking",
                                          ordered =   names(CFA.data),
                                          estimator = "WLSMV",
                                          strict = T)
invariance.model$fit.configural
```
